What makes musicians infer teaching intentions?

### 2022-04-28 paper/manuscript.Rmd
submitted documents
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Tominaga, Knoblich & Sebanz (*submitted*) extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression. We investigated whether and how expert pianists communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound). The results demonstrated that expert pianists systematically modulated their performance by playing slower or by exaggerating relevant aspects of the performance (e.g., producing shorter staccato or producing larger contrast between forte and piano) when intending to teach musical expressive techniques. Therefore, it seems that experts exhibit pedagogical behaviours to highlight crucial performance aspects for potential learners.

@@

## Stimuli
We selected stimuli from the performances obtained in our previous experiments (Tominaga et al., *submitted*). Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files. Multiple pianists played one piece of music with a musical expressive technique of either articulation (*Figure \ref{fig:stim1}*, A) or dynamics (*Figure \ref{fig:stim1}*, B). Articulation refers to the smoothness of sound, which is comprised of legato and staccato. Legato indicates smooth and connected sound whereas staccato indicates sharp and separate sound. Dynamics refers to the loudness of sound, which is comprised of forte and piano. Forte indicates loud sound while piano indicates soft sound. The piece was taken from "A Dozen a Day - Play with Ease in Many Keys" by Edna-Mae Burnam and modified for the experiment. The stimuli were performed around 80 quarter-beats per minute.

In Tominaga et al., (*submitted*), participants were asked to perform the piece with either articulation or dynamics in two different conditions. In the teaching condition, participants were instructed to perform the piece with the designated expressive technique as if they were teaching it to students (e.g., in a lesson). In the performing condition, participants were instructed to perform the piece with the designated expressive technique as if they were performing it to an audience (e.g., in a concert). In Tominaga et al. (*submitted*; Experiment 1), there were 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition. For the current experiment, 96 recordings were chosen from the valid performances. We randomly sampled 24 articulation recordings and 24 dynamics recordings from the teaching condition as well as 24 articulation recordings and 24 dynamics recordings from the performing condition. It is important to note that the recordings from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments (e.g., exaggeration) since we randomly sampled the performances from multiple pianists.

@@

### Accuracy
First, we examined whether participants could accurately recognise the stimuli chosen from the teaching condition in Tominaga et al., (*submitted*; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (*submitted*; Experiment 1) as performing. We compared how accurate participants were against the chance level (50%). Correct responses were either pressing the yes button when listening to teaching recordings or pressing the no button when listening to performing recordings. Incorrect responses were either pressing the yes button when listening to performing recordings or pressing the no button when listening to teaching recordings.

@@

```{r stim-1, out.width = "100%", fig.cap = "\\label{fig:stim1}Stimuli. (A)Articulation. The curved line (slur) indicates legato and the dots indicate staccato. In multiple regression analysis, (1) corresponds to Legato model and (2) corresponds to Staccato model. (B)Dynamics. The symbol `f' denotes forte and the symbol `p' denotes piano. In multiple regression analysis, (3) corresponds to Forte model and (2) corresponds to Piano model. Only the parts composed of 16th notes (i.e., (1), (2), (3), (4)) were used for data analysis.", echo = FALSE}
stim_a <- image_border(image_read(here("paper/image", "stim_a.jpg")), "#FFFFFF", "120x120")
stim_d <- image_border(image_read(here("paper/image", "stim_d.jpg")), "#FFFFFF", "120x120")

@@

## Stimuli
As Experiment 1, we selected stimuli from our previous experiments (Tominaga et al., *submitted*; Experiment 2). The excerpt was taken from ``Sonatina Op.36 (No.3) in C major" by Muzio Clementi and modified for the experiment. The excerpt was performed with either articulation (*Figure \ref{fig:stim2}*, A) or dynamics (*Figure \ref{fig:stim2}*, B). The stimuli were performed around 100 - 120 quarter-beats per minute.

For the current experiment, 72 performances were chosen from the valid performances in Tominaga et al. (*submitted*; Experiment 2). There were 248 valid performances in the teaching condition and 256 valid performances in the performing condition. We randomly sampled 18 articulation performances and 18 dynamics performances from the teaching condition as well as 18 articulation performances and 18 dynamics performances from the performing condition. Again, it is important to note that each performance from the teaching condition did not necessarily exhibit specific features of teaching that we found in the previous experiments (e.g., exaggeration) since we randomly sampled the performances.

@@

```{r stim-2, out.width = "100%", fig.cap = "\\label{fig:stim2}Stimuli. (A)Articulation. The curved line (slur) indicates legato and the dots indicate staccato. In multiple regression analysis, (1) corresponds to Legato model and (2) corresponds to Staccato model. (B)Dynamics. The symbol `f' denotes forte and the symbol `p' denotes piano. In multiple regression analysis, (3) corresponds to Forte model and (2) corresponds to Piano model. Only the 8th notes with expressive notations (i.e., (1), (2), (3), (4)) were used for data analysis.", echo = FALSE}
stim_a_2 <- image_border(image_read(here("paper/image", "stim_a_2.jpg")), "#FFFFFF", "120x120")
stim_d_2 <- image_border(image_read(here("paper/image", "stim_d_2.jpg")), "#FFFFFF", "120x120")

@@

The present study investigated whether and how musicians infer pedagogical intentions by listening to piano recordings. In both Experiment 1 and 2, participants were able to choose correct answers accurately more than chance (50%). However, the results showed that the accuracy was relatively low (52.7 % in Experiment 1; 52.8 % in Experiment 2). This might be because the stimuli were randomly sampled from the teaching and performing condition in Tominaga et al. (*submitted*). There was great variability in the selected recordings from multiple pianists and some of them do not seem to have exhibited the characteristics of teaching performance (e.g., slower demonstration, exaggeration). A possible reason is that some participants had difficulties in situating themselves in a teaching context and therefore did not produce cues.

@@

The piece used in Experiment 2 was from actual sonatinas. Although sonatina pieces are generally aimed to be simple and easy for beginner pianists to play, they add a multitude of musical properties to a performance that is not present in musical scales. Not only do performers produce their communicative intentions such as emotion, but composers can express their feelings by handling various musical notations such as melody, rhythm and harmony [@gabrielsson_2010]. In our study, most of the staccato parts of the piece used in Experiment 2 (Figure, 7 (2)) were comprised of the same repetitive notes. This implied that they could be only played in staccato style. Dynamics may be more independent of the structure of the piece compared to articulation. Therefore, participants might have had difficulties in recognising teaching intentions from articulation in Experiment 2. This would imply that the ease of difficulty with which teaching intentions can be derived vary across different pieces depend on a variety of musical properties.

>>>>

@tominaga_2022a extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression. We investigated whether and how expert pianists communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound). The results demonstrated that expert pianists systematically modulated their performance by playing slower or by exaggerating relevant aspects of the performance (e.g., producing shorter staccato or producing larger contrast between forte and piano) when intending to teach musical expressive techniques. Therefore, it seems that experts exhibit pedagogical behaviours to highlight crucial performance aspects for potential learners.

@@

## Stimuli
We selected stimuli from the performances obtained in our previous experiments [@tominaga_2022a]. Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files. Multiple pianists played one piece of music with a musical expressive technique of either articulation (*Figure \ref{fig:stim1}*, A) or dynamics (*Figure \ref{fig:stim1}*, B). Articulation refers to the smoothness of sound, which is comprised of legato and staccato. Legato indicates smooth and connected sound whereas staccato indicates sharp and separate sound. Dynamics refers to the loudness of sound, which is comprised of forte and piano. Forte indicates loud sound while piano indicates soft sound. The piece was taken from "A Dozen a Day - Play with Ease in Many Keys" by Edna-Mae Burnam and modified for the experiment. The stimuli were performed around 80 quarter-beats per minute.

In @tominaga_2022a, participants were asked to perform the piece with either articulation or dynamics in two different conditions. In the teaching condition, participants were instructed to perform the piece with the designated expressive technique as if they were teaching it to students (e.g., in a lesson). In the performing condition, participants were instructed to perform the piece with the designated expressive technique as if they were performing it to an audience (e.g., in a concert). In Tominaga et al. (2022; Experiment 1), there were 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition. For the current experiment, 96 recordings were chosen from the valid performances. We randomly sampled 24 articulation recordings and 24 dynamics recordings from the teaching condition as well as 24 articulation recordings and 24 dynamics recordings from the performing condition. It is important to note that the recordings from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments (e.g., exaggeration) since we randomly sampled the performances from multiple pianists.

@@

### Accuracy
First, we examined whether participants could accurately recognise the stimuli chosen from the teaching condition in Tominaga et al., (2022; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (2022; Experiment 1) as performing. We compared how accurate participants were against the chance level (50%). Correct responses were either pressing the yes button when listening to teaching recordings or pressing the no button when listening to performing recordings. Incorrect responses were either pressing the yes button when listening to performing recordings or pressing the no button when listening to teaching recordings.

@@

```{r stim-1, out.width = "100%", fig.cap = "\\label{fig:stim1}Stimuli. (A)Articulation. The curved line (slur) indicates legato and the dots indicate staccato. In multiple regression analysis, (1) corresponds to Legato model and (2) corresponds to Staccato model. (B)Dynamics. The symbol `f' denotes forte and the symbol `p' denotes piano. In multiple regression analysis, (3) corresponds to Forte model and (4) corresponds to Piano model. Only the parts composed of 16th notes (i.e., (1), (2), (3), (4)) were used for data analysis.", echo = FALSE}
stim_a <- image_border(image_read(here("paper/image", "stim_a.jpg")), "#FFFFFF", "120x120")
stim_d <- image_border(image_read(here("paper/image", "stim_d.jpg")), "#FFFFFF", "120x120")

@@

## Stimuli
As Experiment 1, we selected stimuli from our previous experiments (Tominaga et al., 2022; Experiment 2). The excerpt was taken from ``Sonatina Op.36 (No.3) in C major" by Muzio Clementi and modified for the experiment. The excerpt was performed with either articulation (*Figure \ref{fig:stim2}*, A) or dynamics (*Figure \ref{fig:stim2}*, B). The stimuli were performed around 100 - 120 quarter-beats per minute.

For the current experiment, 72 performances were chosen from the valid performances in Tominaga et al. (2022; Experiment 2). There were 248 valid performances in the teaching condition and 256 valid performances in the performing condition. We randomly sampled 18 articulation performances and 18 dynamics performances from the teaching condition as well as 18 articulation performances and 18 dynamics performances from the performing condition. Again, it is important to note that each performance from the teaching condition did not necessarily exhibit specific features of teaching that we found in the previous experiments (e.g., exaggeration) since we randomly sampled the performances.

@@

```{r stim-2, out.width = "100%", fig.cap = "\\label{fig:stim2}Stimuli. (A)Articulation. The curved line (slur) indicates legato and the dots indicate staccato. In multiple regression analysis, (1) corresponds to Legato model and (2) corresponds to Staccato model. (B)Dynamics. The symbol `f' denotes forte and the symbol `p' denotes piano. In multiple regression analysis, (3) corresponds to Forte model and (4) corresponds to Piano model. Only the 8th notes with expressive notations (i.e., (1), (2), (3), (4)) were used for data analysis.", echo = FALSE}
stim_a_2 <- image_border(image_read(here("paper/image", "stim_a_2.jpg")), "#FFFFFF", "120x120")
stim_d_2 <- image_border(image_read(here("paper/image", "stim_d_2.jpg")), "#FFFFFF", "120x120")

@@

The present study investigated whether and how musicians infer pedagogical intentions by listening to piano recordings. In both Experiment 1 and 2, participants were able to choose correct answers accurately more than chance (50%). However, the results showed that the accuracy was relatively low (52.7 % in Experiment 1; 52.8 % in Experiment 2). This might be because the stimuli were randomly sampled from the teaching and performing condition in @tominaga_2022a. There was great variability in the selected recordings from multiple pianists and some of them do not seem to have exhibited the characteristics of teaching performance (e.g., slower demonstration, exaggeration). A possible reason is that some participants had difficulties in situating themselves in a teaching context and therefore did not produce cues.

@@

The piece used in Experiment 2 was from actual sonatinas. Although sonatina pieces are generally aimed to be simple and easy for beginner pianists to play, they add a multitude of musical properties to a performance that is not present in musical scales. Not only do performers produce their communicative intentions such as emotion, but composers can express their feelings by handling various musical notations such as melody, rhythm and harmony [@gabrielsson_2010]. In our study, most of the staccato parts of the piece used in Experiment 2 (*Figure \ref{fig:stim2}*, (2)) were comprised of the same repetitive notes. This implied that they could be only played in a staccato style. Dynamics may be more independent of the structure of the piece compared to articulation. Therefore, participants might have had difficulties in recognising teaching intentions from articulation in Experiment 2. This would imply that the ease of difficulty with which teaching intentions can be derived vary across different pieces depend on a variety of musical properties.

### 2022-04-28 paper/manuscript.tex
submitted documents
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Tominaga, Knoblich \& Sebanz (\emph{submitted}) extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression. We investigated whether and how expert pianists communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound). The results demonstrated that expert pianists systematically modulated their performance by playing slower or by exaggerating relevant aspects of the performance (e.g., producing shorter staccato or producing larger contrast between forte and piano) when intending to teach musical expressive techniques. Therefore, it seems that experts exhibit pedagogical behaviours to highlight crucial performance aspects for potential learners.

@@

We selected stimuli from the performances obtained in our previous experiments (Tominaga et al., \emph{submitted}). Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files. Multiple pianists played one piece of music with a musical expressive technique of either articulation (\emph{Figure \ref{fig:stim1}}, A) or dynamics (\emph{Figure \ref{fig:stim1}}, B). Articulation refers to the smoothness of sound, which is comprised of legato and staccato. Legato indicates smooth and connected sound whereas staccato indicates sharp and separate sound. Dynamics refers to the loudness of sound, which is comprised of forte and piano. Forte indicates loud sound while piano indicates soft sound. The piece was taken from ``A Dozen a Day - Play with Ease in Many Keys'' by Edna-Mae Burnam and modified for the experiment. The stimuli were performed around 80 quarter-beats per minute.

In Tominaga et al., (\emph{submitted}), participants were asked to perform the piece with either articulation or dynamics in two different conditions. In the teaching condition, participants were instructed to perform the piece with the designated expressive technique as if they were teaching it to students (e.g., in a lesson). In the performing condition, participants were instructed to perform the piece with the designated expressive technique as if they were performing it to an audience (e.g., in a concert). In Tominaga et al.~(\emph{submitted}; Experiment 1), there were 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition. For the current experiment, 96 recordings were chosen from the valid performances. We randomly sampled 24 articulation recordings and 24 dynamics recordings from the teaching condition as well as 24 articulation recordings and 24 dynamics recordings from the performing condition. It is important to note that the recordings from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments (e.g., exaggeration) since we randomly sampled the performances from multiple pianists.

@@

First, we examined whether participants could accurately recognise the stimuli chosen from the teaching condition in Tominaga et al., (\emph{submitted}; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (\emph{submitted}; Experiment 1) as performing. We compared how accurate participants were against the chance level (50\%). Correct responses were either pressing the yes button when listening to teaching recordings or pressing the no button when listening to performing recordings. Incorrect responses were either pressing the yes button when listening to performing recordings or pressing the no button when listening to teaching recordings.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/stim-1-1} \caption{\label{fig:stim1}Stimuli. (A)Articulation. The curved line (slur) indicates legato and the dots indicate staccato. In multiple regression analysis, (1) corresponds to Legato model and (2) corresponds to Staccato model. (B)Dynamics. The symbol `f' denotes forte and the symbol `p' denotes piano. In multiple regression analysis, (3) corresponds to Forte model and (2) corresponds to Piano model. Only the parts composed of 16th notes (i.e., (1), (2), (3), (4)) were used for data analysis.}\label{fig:stim-1}
\end{figure}

@@

We also performed a one sample \emph{t}-test for each technique separately. For articulation, the mean percentage of correct answers {[}\emph{M} = 50.2, \emph{SD} = 6.55{]} was not significantly different from chance (\emph{t}(19) = 0.14, \emph{p} = .89, cohen's \emph{d} = 0.03). For dynamics, the mean percentage of correct answers {[}\emph{M} = 55.2, \emph{SD} = 7.81{]} was significantly higher than chance (\emph{t}(19) = 2.98, \emph{p} = .01, cohen's \emph{d} = 0.67). A paired \emph{t}-test revealed that there was a significant difference between the two techniques in terms of the accuracy (\emph{t}(19) = -2.12, \emph{p} = .048, cohen's \emph{d} = -0.69), suggesting participants chose correct answers more for dynamics recordings than articulation recordings.

@@

As Experiment 1, we selected stimuli from our previous experiments (Tominaga et al., \emph{submitted}; Experiment 2). The excerpt was taken from ``Sonatina Op.36 (No.3) in C major'' by Muzio Clementi and modified for the experiment. The excerpt was performed with either articulation (\emph{Figure \ref{fig:stim2}}, A) or dynamics (\emph{Figure \ref{fig:stim2}}, B). The stimuli were performed around 100 - 120 quarter-beats per minute.

For the current experiment, 72 performances were chosen from the valid performances in Tominaga et al.~(\emph{submitted}; Experiment 2). There were 248 valid performances in the teaching condition and 256 valid performances in the performing condition. We randomly sampled 18 articulation performances and 18 dynamics performances from the teaching condition as well as 18 articulation performances and 18 dynamics performances from the performing condition. Again, it is important to note that each performance from the teaching condition did not necessarily exhibit specific features of teaching that we found in the previous experiments (e.g., exaggeration) since we randomly sampled the performances.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/stim-2-1} \caption{\label{fig:stim2}Stimuli. (A)Articulation. The curved line (slur) indicates legato and the dots indicate staccato. In multiple regression analysis, (1) corresponds to Legato model and (2) corresponds to Staccato model. (B)Dynamics. The symbol `f' denotes forte and the symbol `p' denotes piano. In multiple regression analysis, (3) corresponds to Forte model and (2) corresponds to Piano model. Only the 8th notes with expressive notations (i.e., (1), (2), (3), (4)) were used for data analysis.}\label{fig:stim-2}
\end{figure}

@@

The present study investigated whether and how musicians infer pedagogical intentions by listening to piano recordings. In both Experiment 1 and 2, participants were able to choose correct answers accurately more than chance (50\%). However, the results showed that the accuracy was relatively low (52.7 \% in Experiment 1; 52.8 \% in Experiment 2). This might be because the stimuli were randomly sampled from the teaching and performing condition in Tominaga et al.~(\emph{submitted}). There was great variability in the selected recordings from multiple pianists and some of them do not seem to have exhibited the characteristics of teaching performance (e.g., slower demonstration, exaggeration). A possible reason is that some participants had difficulties in situating themselves in a teaching context and therefore did not produce cues.

@@

The piece used in Experiment 2 was from actual sonatinas. Although sonatina pieces are generally aimed to be simple and easy for beginner pianists to play, they add a multitude of musical properties to a performance that is not present in musical scales. Not only do performers produce their communicative intentions such as emotion, but composers can express their feelings by handling various musical notations such as melody, rhythm and harmony (Gabrielsson \& Lindström, 2010). In our study, most of the staccato parts of the piece used in Experiment 2 (Figure, 7 (2)) were comprised of the same repetitive notes. This implied that they could be only played in staccato style. Dynamics may be more independent of the structure of the piece compared to articulation. Therefore, participants might have had difficulties in recognising teaching intentions from articulation in Experiment 2. This would imply that the ease of difficulty with which teaching intentions can be derived vary across different pieces depend on a variety of musical properties.

@@

>>>>

Tominaga, Knoblich, and Sebanz (2022) extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression. We investigated whether and how expert pianists communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound). The results demonstrated that expert pianists systematically modulated their performance by playing slower or by exaggerating relevant aspects of the performance (e.g., producing shorter staccato or producing larger contrast between forte and piano) when intending to teach musical expressive techniques. Therefore, it seems that experts exhibit pedagogical behaviours to highlight crucial performance aspects for potential learners.

@@

We selected stimuli from the performances obtained in our previous experiments (Tominaga et al., 2022). Stimuli were produced by actual pianists on a weighed Yamaha MIDI (Musical Instrument Digital Interface) digital piano and recorded as MIDI files. Multiple pianists played one piece of music with a musical expressive technique of either articulation (\emph{Figure \ref{fig:stim1}}, A) or dynamics (\emph{Figure \ref{fig:stim1}}, B). Articulation refers to the smoothness of sound, which is comprised of legato and staccato. Legato indicates smooth and connected sound whereas staccato indicates sharp and separate sound. Dynamics refers to the loudness of sound, which is comprised of forte and piano. Forte indicates loud sound while piano indicates soft sound. The piece was taken from ``A Dozen a Day - Play with Ease in Many Keys'' by Edna-Mae Burnam and modified for the experiment. The stimuli were performed around 80 quarter-beats per minute.

In Tominaga et al. (2022), participants were asked to perform the piece with either articulation or dynamics in two different conditions. In the teaching condition, participants were instructed to perform the piece with the designated expressive technique as if they were teaching it to students (e.g., in a lesson). In the performing condition, participants were instructed to perform the piece with the designated expressive technique as if they were performing it to an audience (e.g., in a concert). In Tominaga et al.~(2022; Experiment 1), there were 453 valid performances (i.e., performances without any pitch errors) from the teaching condition and 436 valid performances from the performing condition. For the current experiment, 96 recordings were chosen from the valid performances. We randomly sampled 24 articulation recordings and 24 dynamics recordings from the teaching condition as well as 24 articulation recordings and 24 dynamics recordings from the performing condition. It is important to note that the recordings from the teaching condition did not necessarily exhibit specific features of teaching performance that we found in our previous experiments (e.g., exaggeration) since we randomly sampled the performances from multiple pianists.

@@

First, we examined whether participants could accurately recognise the stimuli chosen from the teaching condition in Tominaga et al., (2022; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (2022; Experiment 1) as performing. We compared how accurate participants were against the chance level (50\%). Correct responses were either pressing the yes button when listening to teaching recordings or pressing the no button when listening to performing recordings. Incorrect responses were either pressing the yes button when listening to performing recordings or pressing the no button when listening to teaching recordings.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/stim-1-1} \caption{\label{fig:stim1}Stimuli. (A)Articulation. The curved line (slur) indicates legato and the dots indicate staccato. In multiple regression analysis, (1) corresponds to Legato model and (2) corresponds to Staccato model. (B)Dynamics. The symbol `f' denotes forte and the symbol `p' denotes piano. In multiple regression analysis, (3) corresponds to Forte model and (4) corresponds to Piano model. Only the parts composed of 16th notes (i.e., (1), (2), (3), (4)) were used for data analysis.}\label{fig:stim-1}
\end{figure}

@@

We also performed a one sample \emph{t}-test for each technique separately. For articulation, the mean percentage of correct answers {[}\emph{M} = 50.2, \emph{SD} = 6.55{]} was not significantly different from chance (\emph{t}(19) = 0.14, \emph{p} = .89, cohen's \emph{d} = 0.03). For dynamics, the mean percentage of correct answers {[}\emph{M} = 55.2, \emph{SD} = 7.81{]} was significantly higher than chance (\emph{t}(19) = 2.98, \emph{p} = .01, cohen's \emph{d} = 0.67). A paired \emph{t}-test revealed that there was a significant difference between the two techniques in terms of the accuracy (\emph{t}(19) = -2.12, \emph{p} = .05, cohen's \emph{d} = -0.69), suggesting participants chose correct answers more for dynamics recordings than articulation recordings.

@@

As Experiment 1, we selected stimuli from our previous experiments (Tominaga et al., 2022; Experiment 2). The excerpt was taken from ``Sonatina Op.36 (No.3) in C major'' by Muzio Clementi and modified for the experiment. The excerpt was performed with either articulation (\emph{Figure \ref{fig:stim2}}, A) or dynamics (\emph{Figure \ref{fig:stim2}}, B). The stimuli were performed around 100 - 120 quarter-beats per minute.

For the current experiment, 72 performances were chosen from the valid performances in Tominaga et al.~(2022; Experiment 2). There were 248 valid performances in the teaching condition and 256 valid performances in the performing condition. We randomly sampled 18 articulation performances and 18 dynamics performances from the teaching condition as well as 18 articulation performances and 18 dynamics performances from the performing condition. Again, it is important to note that each performance from the teaching condition did not necessarily exhibit specific features of teaching that we found in the previous experiments (e.g., exaggeration) since we randomly sampled the performances.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/stim-2-1} \caption{\label{fig:stim2}Stimuli. (A)Articulation. The curved line (slur) indicates legato and the dots indicate staccato. In multiple regression analysis, (1) corresponds to Legato model and (2) corresponds to Staccato model. (B)Dynamics. The symbol `f' denotes forte and the symbol `p' denotes piano. In multiple regression analysis, (3) corresponds to Forte model and (4) corresponds to Piano model. Only the 8th notes with expressive notations (i.e., (1), (2), (3), (4)) were used for data analysis.}\label{fig:stim-2}
\end{figure}

@@

The present study investigated whether and how musicians infer pedagogical intentions by listening to piano recordings. In both Experiment 1 and 2, participants were able to choose correct answers accurately more than chance (50\%). However, the results showed that the accuracy was relatively low (52.7 \% in Experiment 1; 52.8 \% in Experiment 2). This might be because the stimuli were randomly sampled from the teaching and performing condition in Tominaga et al. (2022). There was great variability in the selected recordings from multiple pianists and some of them do not seem to have exhibited the characteristics of teaching performance (e.g., slower demonstration, exaggeration). A possible reason is that some participants had difficulties in situating themselves in a teaching context and therefore did not produce cues.

@@

The piece used in Experiment 2 was from actual sonatinas. Although sonatina pieces are generally aimed to be simple and easy for beginner pianists to play, they add a multitude of musical properties to a performance that is not present in musical scales. Not only do performers produce their communicative intentions such as emotion, but composers can express their feelings by handling various musical notations such as melody, rhythm and harmony (Gabrielsson \& Lindström, 2010). In our study, most of the staccato parts of the piece used in Experiment 2 (\emph{Figure \ref{fig:stim2}}, (2)) were comprised of the same repetitive notes. This implied that they could be only played in a staccato style. Dynamics may be more independent of the structure of the piece compared to articulation. Therefore, participants might have had difficulties in recognising teaching intentions from articulation in Experiment 2. This would imply that the ease of difficulty with which teaching intentions can be derived vary across different pieces depend on a variety of musical properties.

@@

\leavevmode\vadjust pre{\hypertarget{ref-tominaga_2022a}{}}%
Tominaga, A., Knoblich, G., \& Sebanz, N. (2022). \emph{The sound of teaching music: {Expert} pianists' performance modulations for novices}. {PsyArXiv}. \url{https://doi.org/10.31234/osf.io/wzuyj}
